Meta-analytic approaches and 'new' effect sizes to account for heterogeneous effects in comparative physiology

### 2021-07-08 MS/ms.Rmd
Finished re-writing heterogenity section

```{r tablea, echo = FALSE, tab.cap = "Common effect sizes used throughout meta-analyses in comparative physiology, their associated sampling variances and examples on when they might be used. Note that that a correction factor, J = 1 - (3 /  (4(N1 + N2 - 2) - 1)), is applied to the SMD to correct for small sample effects"}

@@

# Note: It is esssential that you be clear that the function 'compose' is exported from the flextable package. That's because purr also has the same function, so it gets messy.
tablea <- flextable(table_fin)                                                                                %>% 
          flextable::compose(j = 1:4, part = "header", value = as_paragraph(as_b(c("Effect Measure", "Definition", "Sampling Variance", "Examples")))) %>% 
          flextable::compose(j = 2:3, value = as_paragraph(as_equation(c(eqns_yi, eqns_vi))))             %>%
          flextable::compose(j = 4, value = as_paragraph(eg))             %>%
          flextable::width(j = 1, 3)                                                                          %>% 
          flextable::width(j = 2, 2) %>% 
          flextable::width(j = 4, 5)

@@

While heterogenity estimates using $I^2$ measures can be useful for understanding the relative contributions of different factors to effect size variation, prediction intervals might be more appropriate in many cases [@Nakagawa2021c; @Borenstein2019]. Unlike $I^2$, prediction intervals are more holistic and probably more meaningful in the context of meta-analysis. Prediction intervals make use of the standard deviation of the mean instead of the standard error (which is used to calculate confidence intervals) [@Borenstein2019].

>>>>

```{r tablea, echo = FALSE, tab.cap = "Common effect sizes used throughout meta-analyses in comparative physiology, their associated sampling variances and examples on when they might be used."}

@@

footnotes <- c("Notes: J = 1 - \\frac{3}{4\\left(N_{1} + N_{2} - 2\\right) - 1}",
               "SD_{p} = \\sqrt \\frac{\\left( N_{1}-1 \\right)SD_{1}^2 + \\left( N_{2}-1 \\right)SD_{2}^2}{N_{1} + N_{2} - 2}")

# Note: It is esssential that you be clear that the function 'compose' is exported from the flextable package. That's because purr also has the same function, so it gets messy.
tablea <- flextable(table_fin)                                                                                %>% 
          flextable::compose(j = 1:4, part = "header", value = as_paragraph(as_b(c("Effect Measure", "Definition", "Sampling Variance", "Examples")))) %>% 
          flextable::compose(j = 2:3, value = as_paragraph(as_equation(c(eqns_yi, eqns_vi))))             %>%
          flextable::compose(j = 4, value = as_paragraph(eg))             %>%
          flextable::width(j = 1, 3)                                                                          %>% 
          flextable::width(j = 2, 2) %>% 
          flextable::width(j = 4, 5) %>% 
          flextable::footnote(i = 4, j = 1, value = as_paragraph(as_equation(footnotes)),
               ref_symbols = c("a"),
               part = "body", inline = TRUE)

@@

Heterogenity described using $I^2$ measures can be useful for understanding the relative contributions of different factors to effect size variation, however, prediction intervals might be more appropriate in many cases [@Nakagawa2021c; @Borenstein2019]. Unlike $I^2$, prediction intervals (PI's) are probably more meaningful in the context of meta-analysis because they explicitly incorperate measures of dispersion around a mean effect size providing information about the likely effect size one can expect if we were to randomly sample a new population. For example, assume that we were interested in the overall impact of salinity stress in freshwater fish. To tackle this question, we collected experimental studies measuring freshwater fish swim performance under high salinity treatments (~15-20ppm NaCl) compared to freshwater (~0ppm NaCl) controls and used SMD to quantify the magnitude of effect salinity had on swim performance. We conduct a meta-analysis and estimate an overall SMD of 0.50 with a prediction interval of 0.05 to 0.85. The PI indicates that effects can vary widely from as low as an SMD of 0.05 to as high as an SMD 0.95, depending on the population. In otherwords, if we were to repeat a study we would expect a new effect to fall within the range of 0.05 and 0.85, 95\% of the time [@Borenstein2019; @Nakagawa2021c]. This is a very intutive interprettaion of how variable effects are, yet PIs are often not reported in meta-analyses [@Nakagawa2021c].
